Networked Character Devices

### 2011-12-11 report/paper.tex
paper: convert existing figures to grayscale
paper: make listings more suitable this medium

\lstloadlanguages{C}
\lstset{
  language=C,
  basicstyle=\footnotesize,
  numbers=none,
  numberstyle=\footnotesize,
  stepnumber=1,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  title=\lstname,
  frame=single,
  frameround=tttt
}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{arch-03.png}
  \end{center}
  \caption{The basic client-server model of NCD.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{proto.png}
  \end{center}
  \caption{NCD operates over a simple request reply protocol. Bulk data
  immediately follows formal messages, as required.}
  \label{fig:protocol}
\end{figure}

@@

>>>>

\lstloadlanguages{C}
\lstset{
  language=C,
  basicstyle=\tiny,
  numbers=none,
  numberstyle=\footnotesize,
  stepnumber=1,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  float
}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{arch-03-g.png}
  \end{center}
  \caption{The basic client-server model of NCD.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{proto-g.png}
  \end{center}
  \caption{NCD operates over a simple request reply protocol. Bulk data
  immediately follows formal messages, as required.}
  \label{fig:protocol}
\end{figure}

@@

\subsection{Misc}

\subsubsection{udev}

\subsubsection{ncadmin}
